---
title: basic
author: jilung
date: '2018-07-01'
slug: basic
categories:
  - basic
tags:
  - basic
---

# Resource

* Slide: https://docs.google.com/presentation/d/e/2PACX-1vRjb_W1Vo9-zD9F4FmWOiB6K4ezkF6W64OKcX7bZD6ordKvOT-6LFoGi0le-HzT2ABKudDNhr_qKt2x/pub?start=false&loop=false&delayms=3000&slide=id.g2074c710b4_0_293
* 2017/09/24 Updated


# 自R-CRAN安裝套件
* 當使用`install.packages("package_name")`時，就會自[R-cran](https://cran.r-project.org/web/packages/available_packages_by_name.html)搜尋是否有該套件，有的話就會將該套件安裝到你的電腦中。(The package will be downloaded and installed to your computer, BUT not yet loaded into your current environment.)例如：`install.packages("tidyverse")`
* 此時，雖然該套件已經安裝在你的電腦中，但並不代表你現在的程式可以使用它，你必須要使用`library(package_name)`將其匯入或引入目前的程式執行環境中。

```{r}
library(jsonlite)
library(httr)
```





# Try to get data

```{r}
load(url("http://varianceexplained.org/files/trump_tweets_df.rda"))
df <- trump_tweets_df

fliter.df <- df[df$favoriteCount > mean(df$favoriteCount) +2*sd (df$favoriteCount),]
# View(fliter.df)

fliter.df2 <- df[df$retweetCount > mean(df$retweetCount) + 2* sd (df$retweetCount),]

order.df <- df[order(df$favoriteCount, decreasing = TRUE),]
# View(order.df[1:10,])

```

# plotting
```{r}
hist(df$favoriteCount, breaks = 1000)

```


```{r}
df$nchar <-nchar (df$text)
hist(df$nchar, breaks= 1000)

# View(order.df[ ,c(1,3,5,8,10,12)]
# View(order.df[, c("text","favoriteCount")]
# View(df)
```

# Viewing data
```{r}
head(df)
class(df)
str(df)
```



```{r}
class(df$text)
class(df$truncated)
df$truncated
class(df$favoriteCount)
class(df)
mode(df)
?mode
```


# read fb data
```{r}
library(jsonlite)
library(httr)

url <- "https://www.dcard.tw/_api/forums/relationship/posts?popular=true"
res <- fromJSON(content(GET(url), "text"))
# View(res)

fburl <-
	"https://graph.facebook.com/v2.10/DoctorKoWJ?fields=posts&access_token=188730144854871|1lL4a4CTRymAHvoKxnJDQqvqVdc"

res <- fromJSON(content(GET(fburl), "text"))
# View(res$posts$data)
```



```{r}
url1 <- "https://rent.591.com.tw/home/search/rsList?is_new_list=1&type=1&kind=2&searchtype=1&region=1"
res1 <- fromJSON(content(GET(url1), "text"))
all.df <- res1$data$data
```



```{r}

url <- "http://data.taipei/opendata/datalist/datasetMeta/download?id=68785231-d6c5-47a1-b001-77eec70bec02&rid=34a4a431-f04d-474a-8e72-8d3f586db3df"
df <- read.csv(url, fileEncoding = "big5")




```


# df1. take a glance at data.frame
```{r}
# View(df)
head(df)	# get first part of the data.frame
class(df)
str(df)

summary(df)
# look up help
help(summary)
?summary


```


# df2. Dimension of data.frame
```{r}

dim(df)
ncol(df)
nrow(df)
length(df)
```


# df3. data.frame and vectors

```{r}
names(df)
df$發生.現.地點
df$發生時段
length(df$發生時段)
```



# Vector

## Creating vectors

* http://cus93.trade.gov.tw/FSC3040F/FSC3040F?menuURL=FSC3040F
```{r}
country <- c("CN", "US", "JP", "HK", "KR", "SG", "DE", "MY", "VN", "PH", "TH", "AU", "NL", "SA", "ID", "GB", "IN", "FR", "IT", "AE")
buyin <- c(26.142, 12.008, 7.032, 13.646, 4.589, 5.768, 2.131, 2.802, 3.428, 3.019, 1.976, 1.118, 1.624, 0.449, 0.983, 1.302, 1.027, 0.553, 0.670, 0.455)
buyout <- c(22.987, 12.204, 11.837, 7.739, 5.381, 4.610, 2.866, 2.784, 2.414, 2.092, 1.839, 1.788, 1.665, 1.409, 1.391, 1.075, 0.974, 0.899, 0.800, 0.728)

country[c (1,3,5)]


```


## create by sequence
```{r}
a <- seq(11, 99, 11)
a
a[3:length(a)]
a[length(a):3]
b <- 11:20

```

## create by distribution
```{r}
c <- runif(1000, 1, 10) # uniform dist, n=1000
c <- rnorm(10000000, 1, 10) # normal dist, n=1000

# View(country)

plot(density(c))
```


# Take a glance at a vector
```{r}
country
buyin
head(country)
tail(country)
length(country)
# View(country)
```


# Get elements from vectors
```{r}
country[3:7]

# returning elements by index
country[c(1, 3, 5)]
country[c(5, 3, 1)]

a <- seq(11, 99, 11)
a[3:length(a)]
a[length(a):3]
```


# Delete elements from vectors
```{r}

b <- 11:20
b[-(3:5)]
b[-c(1, 3, 5)]

# Without assignment, deletion won't change original vectors
b

# Assign to replace original vectors
b <- b[-(3:5)]
b

a <- seq(11, 99, 11)
a <- a[-c(1, 3, 5)]
a


```



# Concatenate two or three vectors

```{r}
a <- 1:10
a <- c(a, 11)
a
b
a <- c(a, b)
a
a <- c(a, a, b)
a

```




# Arithmetic operations

```{r}
a <- 11:19
a + 3
a / 2

a %% 2
a %/% 2
a %% 2== 0
a %% 2 != 0
a[a%% 2 == 0]
a[a%%2 != 0]
a <- a %% 2 	# modular arithmetic, get the reminder
a <- a %/% 2 	# Quotient


```



# Logical comparison

```{r}
a %% 2 == 0 	# deteting odd/even number
a %% 2 != 0
a[a%%2==0]
a > b
buyin > mean(buyin)
buyin > buyout

TRUE == T 		# == equal to,
TRUE != F    	# != Not equal to

any(a>11) # is there any element larger than 1
all(a>11) # are all elements larger than 1


# two methods to filter data from vectors, by index vector or a logical vector with equal length
a <- seq(11, 55, 11)
a[c(T, F, T, F, T)]
a[a%%2==1]
# a
a%%2
a%%2==1

# which will return "index-of"
a[which(a%%2==1)]
which(a%%2==1)

ac <- c("你好","你好棒棒","你好棒","你真的好棒")
ac[nchar(ac)>3]

```




# Practice

```{r}
x.a <- rnorm(1000, 1, 10)

# 1.1 Filter out extreme values out of two standard deviations


# 1.2 Plotting the distribution of the remaining vector x.a


# 1.3 Calculate the 25% 50% and 75% quantile of vector x.a. You may google "quantile r"


# 1.4 Get the number between 25% to 75%



x.b <- c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j", "k")

# 2.1 Get only elements at odd positions

# 2.2 Truncate the first 2 elements and the last 2 elements



```


# Sorting


```{r}
c <- c(33, 55, 22, 13, 4, 24)


# Sort it directly
sort(c)


# Get the order
order(c) # 5, 4, 3, 6, 1, 2 <- the min to max sequence of original index
c[order(c)] # will produce identical vector with sort(c)

# assign to replace c
c <- sort(c)



```

# Math functions

```{r}
a <- 11:19
min(a); max(a); mean(a); median(a); sd(a)
log2(a)
log1p(a)
?log1p


```


# Mode of vector

```{r}

mode(country)				# character
mode(buyin)					# numeric
mode(buyin > mean(buyin))	# logical

buyinc <- c("26.142", "12.008", "7.032", "13.646", "4.589")
mode(buyinc)				# character


```

# Mode conversion

```{r}

# character > numeric > logical

buyinc <- as.character(buyin)
buyinn <- as.numeric(buyinc)

a <- seq(11, 99, 11)
a <- c(a, "100")

a <- seq(11, 99, 11)
sum(a%%2==1)
```


# string concatenation

```{r}
a <- seq(11, 55, 11)
paste("A", a)		# concatenate
paste0("A", a)		# concatenate
```


# Combine 3 vectors to a dataframe

```{r}
df <- data.frame(country, buyin, buyout)

df <- data.frame(country, buyin, buyout, stringsAsFactors = FALSE)
str(df)


#df [列,行]
```


# df Arithmetic operatoins between variables
```{r}
df$sub <- df$buyin - df$buyout

```


# df Filtering and selection

```{r}
df
names(df)

# filter row data by column value
df[df$buyin > df$buyout,]
df[df$buyin > df$buyout,]$country
df[df$buyin > df$buyout,1]

# 1 row == a data.frame with only one data entry
class(df[df$buyin > df$buyout,1])
class(df[,1]) # character vector
class(df[1,]) # data.frame
class(unlist(df[1, -1])) # filter the 1st row and select all columns except 1


```




# Sort data.frame

```{r}
# sort rows by df$buyin column
df.sorted <- df[order(df$buyin),]
# View(df.sorted)

# sort rows in decreasing order
df.sorted <- df[order(df$buyin, decreasing = T),]

# add - to column in order() can sort in decreasing order
df.sorted <- df[order(-df$buyin),]
# View(df.sorted)

a <- c(5, 5, 5, 5, 4, 4, 4, 3, 3, 1, 1, 1, 2, 2, 2)
b <- c(3, 3, 3, 4, 4, 4, 2, 2, 2, 4, 4, 1, 4, 1, 1)
df2 <- data.frame(a, b)

# sort df2 in orders of decreasing b then increasing a
df2 <- df2[order(df2$a, -df2$b),]


```


# plot

```{r}
# plot(df) # raise error, 1st column is a character vector
plot(df[, 2:3])
plot(df[1:10, 2:3])
text(buyin, buyout, labels=country, cex= 0.5, pos=3)
lines(1:25, 1:25, col='red')

dev.new()


```

